---
title: "DV_RProject2"
output: html_document
---
**Authors: Rolando Melendez, Hyunji Seo, Catherine Tu**

##This is how our RStudio is configured:
```{r}
sessionInfo()
```
***
##Program file structure
  00 Doc - contains .Rmd and .html 
  
  01 Data - contains the code to Extract, Transform, and Load our data 
  
  02 Data Wrangling - contains our workflows and the code for the visualizations 

***  
##Data summary and subset
```{r}
#Shows the subset and summary of the data frame
source("../01 Data/R_Load.R", echo = TRUE)
```

####Explanation of Data:
This data relates to the direct marketing campaign of a Portuguese bank to have people subscribe to a term deposit at their institution. The campaign had gathered data regard their campaign efforts, individuals' demographics, and external socioeconomic situations at the time of the campaign. 

***
##Bank Effort Visualization
```{r}
#Shows the subset and summary of the data frame
source("../02 Data Wrangling/BankEffort_PD.R", echo = TRUE)
```

####Method: 
  We took our original data frame and piped it to mutate in order to seperate the outcomes into percentiles based on duration of the marketing call.Then pipe into select to show only past marketing effectiveness, the duration of the marketing call, the outcome of the whole campaign, and the given percentiles. Lastly pipe to filter to show only the respective percentiles (below 20 and above 80).
  For a better view at the data two more plots were added. The first showing the scope of only what is below the 20th percentile, and the second showing the scope of only what is above the 80th percentile
  All of the plots were faceted in order to seperate yes and no responses for clarity.

####Findings:
What was found was that the higher in the percentile of call duration the more likely the individual was to subscribe a term deposit for the issuing bank. The ranges below the 20th percentile were almost wholly those who rejected the term deposit. The ranges above the 80th percentile were substantially more inclined to take the offer on the term deposit. All this still holds regardless of the outcome of the past marketing campaign. Whether past outcome was a success, a failure, or even non-existent, this trend seems to be the same. One other small trend was that if in the past the marketing failed there was more inclination to fail this time, this not so true about successes.

***

##Demographics Visualization
```{r}
#Shows the subset and summary of the data frame
source("../02 Data Wrangling/Demographics_AHP.R", echo = TRUE)
```

####Method:
The question that we are trying to ask with these visualizations and R workflow is "What are the effects of age and other current loans on one's williness to apply for a term deposit?" 

The R workflow for these visualizations looks for statistical measures (mean age, median age, standard deviation of age, and total count) of the sampled population, grouped by their current loans and their decision to apply for a term deposit with the bank.

The two visualizations show how the target market of the bank's marketing campaign ranged in age based on their current loans, and they compare the size and proportion of those who successfully subscribed for a term deposit after the campaign to those who did not subscribe.
The first visualization is a histogram that utilizes facet_grid to graph the count of the campaign target population's ages based on if they have a housing loan, if they have a personal loan and how they responded to the marketing campaign.
The second visualization is a density plot that compares the relative density of age of those who subscribed to the term deposit to those who did not. This second visualization also uses facet_grid to further divide the two groups of respondents based on their current loan situation.

####Findings:
Through the histogram visualization, we find that relative to those who have personal loans, those who do not have personal loans are more likely to subscribe to the term deposit regardless of if they have a housing loan. From the histogram, it is not clear whether this increase in campaign effectiveness is based on a real correlation between personal loan situations and willingness to subscribe to a term deposit, or if it is simply because much more of the data population do not have personal loans.

The density plot visualization helps to better look into the correlation between personal loans and willingness to subscribe to a term deposit. Through this visualization, we conclude that age plays a role in the campaign response of those who do and do not have personal loans. We find that those who currently do not have personal loans are more willing to subscribe to a term deposit if they are in their lower-30s (in age) than those who already have personal loans. This is best showcased through the differences in density plots of those who have housing loans and do not have personal loans to those who have both housing and personal loans (top right and bottom right graphs). 

***

##Socioeconomic Visualization
```{r}
#Shows the subset and summary of the data frame
source("../02 Data Wrangling/SocioEconomic_EC.R", echo = TRUE)
```

####Method:

####Findings:
** will edit later
Basically, the first two graphs are optional, and are meant to show that there are comparable number of responses across education and marital status. The third graph is the focus, and is meant to indicate that as education level increases, age is no longer a significant factor in determining whether people accepted or declined to subscribe to term deposit. This indicates that younger people are more likely to be influenced by marketing if their education level is higher.
***

