---
title: "DV_RProject2"
output: html_document
---
**Authors: Rolando Melendez, Hyunji Seo, Catherine Tu**

##This is how our RStudio is configured:
```{r}
sessionInfo()
```
***
##Program file structure
  00 Doc - contains .Rmd and .html 
  
  01 Data - contains the code to Extract, Transform, and Load our data 
  
  02 Data Wrangling - contains our workflows and the code for the visualizations 

***  
##Data summary and subset
```{r}
#Shows the subset and summary of the data frame
source("../01 Data/R_Load.R", echo = TRUE)
```
***
##Bank Effort Visualization
```{r}
#Shows the subset and summary of the data frame
source("../02 Data Wrangling/BankEffort_PD.R", echo = TRUE)
```

####Method: 
  We took our original data frame and piped it to mutate in order to seperate the outcomes into percentiles based on duration of the marketing call.Then pipe into select to show only past marketing effectiveness, the duration of the marketing call, the outcome of the whole campaign, and the given percentiles. Lastly pipe to filter to show only the respective percentiles (below 20 and above 80).
  For a better view at the data two more plots were added. The first showing the scope of only what is below the 20th percentile, and the second showing the scope of only what is above the 80th percentile
  All of the plots were faceted in order to seperate yes and no responses for clarity.

####Findings:
What was found was that the higher in the percentile of call duration the more likely the individual was to purchase a term loan from the issuing bank. The ranges below the 20th percentile were almost wholly those who rejected the term loan. The ranges above the 80th percentile were substantially more inclined to take the offer on the term loan. All this still holds regardless of the outcome of the past marketing campaign. Whether past outcome was a success, a failure, or even non-existent, this trend seems to be the same. One other small trend was that if in the past the marketing failed there was more inclination to fail this time, this not so true about successes.

***

##Demographics Visualization
```{r}
#Shows the subset and summary of the data frame
source("../02 Data Wrangling/Demographics_AHP.R", echo = TRUE)
```

####Method:

####Findings:

***

##Socioeconomic Visualization
```{r}
#Shows the subset and summary of the data frame
source("../02 Data Wrangling/SocioEconomic_EC.R", echo = TRUE)
```

####Method:

####Findings:
** will edit later
Basically, the first two graphs are optional, and are meant to show that there are comparable number of responses across education and marital status. The third graph is the focus, and is meant to indicate that as education level increases, age is no longer a significant factor in determining whether people accepted or declined the term loan. This indicates that younger people are more likely to be influenced by marketing if their education level is higher.
***

