---
title: "DV_RProject2"
output: html_document
---
**Authors: Rolando Melendez, Hyunji Seo, Catherine Tu**

##This is how our RStudio is configured:
```{r}
sessionInfo()
```
***
##Program file structure
  00 Doc - contains .Rmd and .html 
  
  01 Data - contains the code to Extract, Transform, and Load our data 
  
  02 Data Wrangling - contains our workflows and the code for the visualizations 

***  
##Data summary and subset
```{r}
#Shows the subset and summary of the data frame
source("../01 Data/R_Load.R", echo = TRUE)
```
***
##Bank Effort Visualization
```{r}
#Shows the subset and summary of the data frame
source("../02 Data Wrangling/BankEffort_PD.R", echo = TRUE)
```

####Method: 
  We took our original data frame and piped it to mutate in order to seperate the outcomes into percentiles based on duration of the marketing call (Done twice; once for higher percentile and once for lower percentile).Then pipe into select to show only past marketing effectiveness, the duration of the marketing call, and the outcome of the whole campaign. Lastly pipe to filter to get the respective percentiles.
  We also saw it fit to seperate the data into indiviual yes or no visualizations for the outcome of the campiagn. This just for ease of distinction. 
  For plotting those who said no, we took our original data frame and piped it to mutate to seperate the outcomes into percentiles based on duration of the marketing call. Then we piped into select to show only past marketing effectiveness, the duration of the marketing call, and the outcome of the whole campaign, then piped that into filter to show only those who said no and below the 40th percentile.
  For plotting those who said yes, we took our original data frame and piped it to mutate to seperate the outcomes into percentiles based on duration of the marketing call. Then we piped into select to show only past marketing effectiveness, the duration of the marketing call, and the outcome of the whole campaign, then piped that into filter to show only those who said yes and above the 80th percentile.

####Findings:
What was found was that the higher in the percentile of call duration the more likeley the individual was to purchase a term loan from the issuing bank. The ranges below the 40th percentile were almost wholly those who rejected the term loan. The ranges above the 80th percentile were substantially more inclined to take the offer on the term loan. All this still holds regardless of the outcome of the past marketing campaign. Whether past outcome was a success, a failure, or even non-existent, this trend seems to be the same.

***

##Demographics Visualization
```{r}
#Shows the subset and summary of the data frame
source("../02 Data Wrangling/Demographics_AHP.R", echo = TRUE)
```

####Method:

####Findings:

***

##Socioeconomic Visualization
```{r}
#Shows the subset and summary of the data frame
source("../02 Data Wrangling/SocioEconomic_EC.R", echo = TRUE)
```

####Method:

####Findings:

***

